---
author: "Min-Jung Jung"
date: "11/27/2021"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo = FALSE, eval = FALSE}
rmarkdown:: render("_Rmd/2021-11-27-Reflection-Blog-Post.Rmd",
                   output_format = "github_document",
                   output_dir = "../mjung5.github.io/_posts", 
                   output_options = list(html_preview = FALSE, keep_html = FALSE)
                   )
```

First of all, I cannot believe I am writing this blog to wrap up the ST558 class. I felt like I was riding a roller coaster throughout this semester. Once I felt comfortable in one area, a new topic was introduced, and I was challenged again to learn new material. There were so many topics to cover, but I know that I am just a beginner in the world of R and that there is much to come. Nonetheless, I am very glad that I took this class and could learn about R. 

•	What (if anything) has changed about what you think a data scientist is and what they do?
My thoughts on being a data scientist haven’t changed much, but I have definitely broadened my idea about the role of a data scientist. Beyond handling data for analysis, I am impressed by how data scientists continuously communicate with others by sharing their work, improving analyses together, and presenting the outcomes to the public. Moreover, I learned the importance of using machine learning to reduce time and increase efficiency in performing analyses.  

•	What your current thoughts are in terms of using R for data science - do you think you'll continue to use R going forward?  Why or why not?
My current job does not require advanced data analysis, so I am not sure how to keep up the knowledge that I have learned from this course. However, I will definitely challenge myself to continue to learn about R and to practice updating my GitHub. One thing I observed from taking this class is that people are freely updating their GitHub with very simple analyses and data sets of their interest. 

•	What things are you going to do differently in practice now that you've had this course?
I love R markdown! R markdown gave me so much flexibility to manipulate data, running analyses, and producing the results in different types of documentation. Currently, I mainly use excel and word files, but I may use R to organize my data and write up my reports in the future. Also, many of my colleagues are social science researchers and need of help from statisticians/data scientists to analyze their data. I will begin collaborating and working with them to get involved in research again.  
