---
title: "Programming Background"
author: "Min-Jung Jung"
date: "9/11/2021"

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.path = "../images/")

```
```{r, echo = FALSE, eval = FALSE}
rmarkdown:: render("2021-9-11-Second-Blog-Post.Rmd",
                   output_format = "github_document",
                   output_dir = "../../mjung5.github.io/_posts", 
                   output_options = list(html_preview = FALSE, keep_html = FALSE)
                   )



```

## R and SAS

What are your thoughts on R vs whatever other software you've used?  What functionality do you like about R? 

R is a very interesting programming language.  I feel like it is a very interactive and flexible program in which there are many ways to get to my outcomes.  Even though it has a higher learning curve and I had to learn from the basic skills, like downloading packages and finding paths to search the files I want to use, I was able to find great amount of resources from various community support groups in the public.  SAS is also a user friendly statistical analytics program, but it is somewhat more rigid and quite syntax based. SAS reports are in graphs, tables, etc., but R reports are in more visual formats and can even include pictures. One interesting aspect about R is that R studio and github can communicate, so I can manage the blog through R markdown. 

What parts do you miss about your other language?

SAS was very beneficial for handling large amounts of raw data and advanced and predictive analysis. Also, I did not have to deal with downloading new packages or updating existing packages. 

Do you consider R a difficult language to learn?

To be honest, R is difficult to learn, and I am spending quite a large amount of time every week to understand the materials and to complete the homework. However, I am not sure if R is a difficult language to learn compared to other languages. I only learned SAS, and SAS was also difficult at the beginning but did get better once I became used to the language and program.  One thing I can say is that I am glad I am taking an R class and that I am learning to be part of a data scientist group.  


## Example R Markdown output

You can also embed plots, for example:

```{r longley, echo=FALSE}
plot(longley)
```


